Persistence in functional topology: local-connectivity, q-tameness and a correction to a theorem of Morse

### 2021-04-15 connectivity.tex
Replace sublevel filtration to sublevel set filtration
we will talk about q-tame filtrations not just p-modules

\begin{prop}
	Let $(X, f)$ be a sublevel filtration. If each sublevel set is compact and $\HLC$ with respect to integral singular homology, then its singular persistence module is p.f.d. in every degree, in particular q-tame.
\end{prop}

Having each sublevel set being $\HLC$ is in many cases too restrictive.
We would like a relative condition for sublevel filtrations to be sufficient to ensure the q-tameness of the associated persistence module.
The following definitions are motivated by Morse's work, please consult Section~\ref{s:historical} for their relation to his original statements.

\begin{defi} \label{defi:local_connectedness_filtrations}
	For a fix homology theory $\H$. A sublevel filtration $(X,f)$ is said to be $\HLC$ if for any $\epsilon > 0$, $x \in X$, and $V$ an open neighborhood of $x$, there is a $\delta \in (0, \epsilon)$ and a neighborhood $U$ of $x$ such that $U \subseteq V$ and
	\begin{equation*}
	X_{\leq f(x) + \delta + c} \cap U \to X_{\leq f(x) + \epsilon + c} \cap V
	\end{equation*}
	is $\HT$ for every $c \geq 0$.
	We also consider a weaker version, referred to as \textit{weakly} $\HLC$, defined as above with $c = 0$.
\end{defi}

@@

\begin{thm} \label{t:strong local connectenss implies q-tameness}
	Morse filtrations which are $\HLC$ give rise to q-tame persistence modules for any homology theory.
\end{thm}

>>>>

\begin{prop}
	Let $(X, f)$ be a sublevel set filtration. If each sublevel set is compact and $\HLC$ with respect to integral singular homology, then its singular persistence module is p.f.d. in every degree, in particular q-tame.
\end{prop}

Having each sublevel set being $\HLC$ is in many cases too restrictive.
We would like a relative condition for sublevel set filtrations to be sufficient to ensure the q-tameness of the associated persistence module.
The following definitions are motivated by Morse's work, please consult Section~\ref{s:historical} for their relation to his original statements.

\begin{defi} \label{defi:local_connectedness_filtrations}
	For a fix homology theory $\H$. A sublevel set filtration $(X,f)$ is said to be $\HLC$ if for any $\epsilon > 0$, $x \in X$, and $V$ an open neighborhood of $x$, there is a $\delta \in (0, \epsilon)$ and a neighborhood $U$ of $x$ such that $U \subseteq V$ and
	\begin{equation*}
	X_{\leq f(x) + \delta + c} \cap U \to X_{\leq f(x) + \epsilon + c} \cap V
	\end{equation*}
	is $\HT$ for every $c \geq 0$.
	We also consider a weaker version, referred to as \textit{weakly} $\HLC$, defined as above with $c = 0$.
\end{defi}

@@

\begin{thm} \label{t:strong local connectenss implies q-tameness}
	Morse filtrations which are $\HLC$ are q-tame for any homology theory.
\end{thm}

### 2021-04-15 introduction.tex
Replace sublevel filtration to sublevel set filtration
we will talk about q-tame filtrations not just p-modules

To obtain q-tameness of the associated persistence module, the most delicate of the conditions imposed on a sublevel filtration are forms of local-connectivity.
In their development of functional topology and its applications to minimal surface theory, Morse and Tompkins presented certain forms of local-connectivity claimed to imply q-tameness; unfortunately, neither the proofs nor the statements are correct.
Please consult Section~\ref{s:historical} for more details on this problem and its history.

>>>>

To obtain q-tameness of the associated persistence module, the most delicate of the conditions imposed on a sublevel set filtration are forms of local-connectivity.
In their development of functional topology and its applications to minimal surface theory, Morse and Tompkins presented certain forms of local-connectivity claimed to imply q-tameness; unfortunately, neither the proofs nor the statements are correct.
Please consult Section~\ref{s:historical} for more details on this problem and its history.

### 2021-04-15 persistence.tex
Add section by section to intro
Replace sublevel filtration to sublevel set filtration
we will talk about q-tame filtrations not just p-modules

\section{Persistence}

@@

A \textit{sublevel filtration} is a pair $(X, f)$ with $X$ a Hausdorff space and $f$ a real-valued function on $X$.
For any $t \in \R$, the \textit{$t$-sublevel set} is defined by 
\begin{equation*}
X_{\leq t} = f^{-1}((-\infty, t]).
\end{equation*}

@@

A sublevel filtration $(X, f)$ is said to be a \textit{Morse filtration} if $X$ is a locally compact space and $X_{\leq t}$ is compact for every $t \in \R$.
Notice that this condition implies, since $X$ is Hausdorff, that $f$ is \textit{lower semi-continuous}, i.e, the preimage of open sets of the form $(t, +\infty)$ is open.

>>>>

\section{Sublevel filtrations and persistence theory} \label{s:persistence}

@@

A \textit{sublevel set filtration} is a pair $(X, f)$ with $X$ a Hausdorff space and $f$ a real-valued function on $X$.
For any $t \in \R$, the \textit{$t$-sublevel set} is defined by 
\begin{equation*}
X_{\leq t} = f^{-1}((-\infty, t]).
\end{equation*}

@@

A sublevel set filtration $(X, f)$ is said to be a \textit{Morse filtration} if $X$ is a locally compact space and $X_{\leq t}$ is compact for every $t \in \R$.
Notice that this condition implies, since $X$ is Hausdorff, that $f$ is \textit{lower semi-continuous}, i.e, the preimage of open sets of the form $(t, +\infty)$ is open.
